Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-12 index.Rmd
tool update + copyright

@@

@@

if(T) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  library("shiny") 
  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  library("reshape")
  library("ggplot2")
}

source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("../FinanceLibraries/heatmapOutput.R") 
source("../FinanceLibraries/shiny_plots.R")

@@

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the buttons which will appear below at any time.

@@

You can select some filters for the dataset. All analyses below will be done only for the companies that are selected.

@@

Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below. The maximum selected should be larger than the minimum, else the maximum is automatically set to 10e6:

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(BUYBACK_DATA_TOOL$Market.Cap)))), selected = as.character(ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))), width = "1000px")
```

@@

  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending & scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max)

  list(
    BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
    returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
    DatesMonth  = DatesMonth[,useonly_report],
    subset = useonly_report
  )
})

@@

This tool allows the user to explore descriptive statistics of some of the key firm characteristics. When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (e.g. for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper. Otherwise it is the raw value of the firm characteristic.

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                           feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

### Industry Robustness Analysis of U-Index

Two types of robustness analysis has been considered in the paper: over different time periods, and across industries. We can select industries to remove here (make sure there are enough data left for the analysis):

@@

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,inline=TRUE) 
```
<br>
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_industry","Enter the quantile to use to define High and Low Firms for this analysis:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

```{r, eval=TRUE, echo = FALSE}

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
  #quantile_used_ind = as.numeric(0.2)
  quantile_used_ind = as.numeric(input$quantile_used_industry)

  res = round(cbind(
    car_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
  #quantile_used_ind = as.numeric(0.2)
  quantile_used_ind = as.numeric(input$quantile_used_industry)

  res = round(cbind(
    calendar_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results,
    calendar_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable_industry()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable_industry()
                         }))    
    ),style='width: 100%;'))
```

@@

The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size). This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not discussed in the paper.

```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = acceptaple_features[4], width = "1000px")

selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")

@@

  res = round(cbind(
    car_table(returns_by_event_monthly[, Low_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(returns_by_event_monthly[, High_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]

@@

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))

  res = round(cbind(
    calendar_table(returns_by_event_monthly[, Low_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
    calendar_table(returns_by_event_monthly[,High_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
  ),2)[reported_times,]

@@

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
                         }))
    ),style='width: 100%;'))
```

@@

### Customized Buyback Index

@@

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4], width = "425px"),
           checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features,selected ="None", width = "425px"),
           checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
    ),
    column(6,
           selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

selectInput("quantile_used_all","Enter the quantile to use to define High and Low Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

<br> 
Here are the results for your new index:

@@

  Index_score = thefeature1 + 
    ifelse(input$characteristic_irats2 != "None",thefeature2,0)+ 
    ifelse(input$characteristic_irats3 != "None",thefeature3,0) + 
    ifelse(input$characteristic_irats4 != "None",thefeature4,0) + 
    ifelse(input$characteristic_irats5 != "None",thefeature5,0) + 
    ifelse(input$characteristic_irats6 != "None",thefeature6,0)
  Index_score

@@

  res = round(cbind(
    car_table(returns_by_event_monthly[, Low_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(returns_by_event_monthly[, High_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

@@

  res = round(cbind(
    calendar_table(returns_by_event_monthly[, Low_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
    calendar_table(returns_by_event_monthly[,High_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
  ),2)[reported_times,]

>>>>

<!--
 Copyright 2015, INSEAD
 by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
 Dual licensed under the MIT or GPL Version 2 licenses.  -->

@@

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 1 when run localy, 1 when deployed on a shinyapps server)

run_shiny_tool = 0

@@

if(run_shiny_tool) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  library("shiny") 
  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  #library("reshape")
  library("ggplot2")
}

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("interactive_tool_files/heatmapOutput.R")

@@

This is an interactive tool for the article [Volatility and the Buyback Anomaly](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** (work in progress) by clicking the button below at any time.

@@

You can select some filters for the dataset. All analyses below will be done only for the events that are selected.

@@

Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below. The maximum selected should be larger than the minimum, else the maximum is automatically set to infinity:

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), 10e10)), selected = as.character(10e10), width = "1000px")
```

We can also see the effects of removing some industries: we can select industries to remove here (make sure there are enough data left for the analysis):

```{r, eval=TRUE, echo = FALSE}
selectInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,multiple=TRUE,width="100%") 
```
<br>

@@

  useonly_industry = !(BUYBACK_DATA_TOOL$Industry_name %in% input$industry)

  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending &
                           scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & 
                           scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max &
                           useonly_industry)

  list(
    BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
    returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
    DatesMonth  = DatesMonth[,useonly_report],
    value.weights = value.weights[useonly_report],
    subset = useonly_report
  )
})

@@

This tool allows the user to explore descriptive statistics of some of the key firm characteristics. When the name of the firm characteristics ends with ".Score" it is the percentile (0 to 1) relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper. Otherwise it is the raw value of the firm characteristic.

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index"),
  mainPanel(
    navlistPanel(
      tabPanel("Histogram",
               busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
               renderPlot({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (!is.numeric(feature))
                   feature = 1
                 hist(feature, density = 100, breaks = 100)
               })),
      tabPanel("Summary Statistics",
               renderDataTable({
                 feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                 feature = feature[!is.na(feature)]
                 if (length(unique(feature)) > 20 & is.numeric(feature)){
                   res = t(round(as.matrix(summary(feature)),2))
                   colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                 }
                 if (is.character(feature) | length(unique(feature)) <= 20){
                   tmp = table(feature)
                   res = t(as.matrix(tmp))
                 }
                 as.data.frame(res)
                 #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                 #print(m1,'chart')
               })
      ),
      widths = c(3, 9)),
    style='width: 100%;'))
```

### The EU-Index

For the subset of events selected the High/Low EU index events (for the selected thresholds) have the abnormal returns below:

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("high_EU_index_thres","Enter the EU index threshold above which (>=) we define the High EU-Index firms (need minimum 10 firms High EU firms):", choices = sort(unique(BUYBACK_DATA_TOOL$EU.Index)), selected = "5", width = "1000px")
```

```{r, eval=TRUE, echo = FALSE}
selectInput("low_EU_index_thres","Enter the EU index threshold below which (<=) we define the Low EU-Index firms (need minimum 10 firms Low EU firms):", choices = sort(unique(BUYBACK_DATA_TOOL$EU.Index)), selected = "1", width = "1000px")
```

@@

```{r, eval=TRUE, echo = FALSE}
EU_index_table <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]
  res = matrix(table(thefeature),nrow=1)
  colnames(res) <- paste("EU Index", names(table(thefeature)), sep=": ")
  rownames(res) <- "# of Events"
  res
})

feature_IRATStable_industry <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

  high_EU_index_thres = as.numeric(input$high_EU_index_thres)
  low_EU_index_thres = as.numeric(input$low_EU_index_thres)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres
  if (sum(High_feature_events) < 10)
    High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres-1

  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= low_EU_index_thres
  if (sum(Low_feature_events) < 10)
    Low_feature_events = !is.na(thefeature) & scrub(thefeature) <= Low_feature_events+1

  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low EU: CAR", "t-stat","p-value", "High EU: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "EU.Index")]]

  high_EU_index_thres = as.numeric(input$high_EU_index_thres)
  low_EU_index_thres = as.numeric(input$low_EU_index_thres)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres
  if (sum(High_feature_events) < 10)
    High_feature_events = !is.na(thefeature) & scrub(thefeature) >= high_EU_index_thres-1

  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= low_EU_index_thres
  if (sum(Low_feature_events) < 10)
    Low_feature_events = !is.na(thefeature) & scrub(thefeature) <= Low_feature_events+1

  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
  ),2)[reported_times,]
  colnames(res) <- c("Low EU: CAL", "t-stat","p-value", "High EU: CAL", "t-stat","p-value")
  as.data.frame(res)
})

fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Number of Firms per EU Index Value",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 EU_index_table()
               })),
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_IRATStable_industry()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_CALtable_industry()
               })),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size). This tool allows the user to study the effects of combining any of these firm characteristics, as well as others not discussed in the paper. We consider here high/low events defined using the quantiles of the selected event charactetistic.

```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")

selectInput("quantile_used","Enter the quantile to use to define High (>=) and Low (<=) Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")

@@

  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]

@@

feature_CALtable <- reactive({
   thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]

  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
  ),2)[reported_times,]

@@

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    navlistPanel(
      tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_IRATStable()
               })),
      tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
               busyIndicator("Calculating results ...",wait = 0),
               renderTable({
                 feature_CALtable()
               })),
      tabPanel("Cumulative Abnormal Returns,High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(High_feature_Hedged_react())
               })),
      tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderDygraph({
                 pnl_plot_interactive(Low_feature_Hedged_react())
               })),
      tabPanel("Monthly and Yearly Returns, High, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(High_feature_Hedged_react())))
               )),
      tabPanel("Monthly and Yearly Returns, Low, 12m hold",
               busyIndicator("Calculating results ...",wait = 0),
               renderUI(
                 HTML(renderHeatmapX(pnl_matrix(Low_feature_Hedged_react())))
               )),
      widths = c(3, 9)),style='width: 100%;'))
```

@@

### Customized Buyback Indices

@@

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = "EU.Index", width = "425px"),
           checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features,selected ="None", width = "425px"),
           checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
    ),
    column(6,
           selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low, <=), 1 (middle), 2 (High, >=) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

selectInput("quantile_used_all","Enter the quantile to use to define High (>=) and Low (<=) Firms for the total index created (sum of the scores of the firm characteristics selected):", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

<br> 
Here are the results for your new customized index:

@@

  Index_score

@@

  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[, High_feature_events],
              DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

@@

  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[, Low_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[Low_feature_events])$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events],
                   DATASET_NEW()$BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = DATASET_NEW()$value.weights[High_feature_events])$results
  ),2)[reported_times,]
